### 2017-05-30 paper.tex
Draft of Rule 9

@@

\item
  FIXME: The lesson is a beginning, not an end, so point them at similar material and where to go next.

\item
  FIXME: Make it part of a much broader conversation.

>>>>

Most learners are unlikely to completely absorb the topic you are trying to
present using only your lesson.
There are many angles and approaches for any given topic.
Make an attempt to find these alternative resources and offer them at strategic points in the lesson,
and collect them at the end.
Some learners prefer different material styles, so seek out textbooks, technical
documentation, videos and web pages which may present the material in alternative styles.
If a community or discussion forum exists for the topic, be sure to include these resources.

Beyond the topic of your lesson, learners can go in many directions after completion.
Provider learners with extensions and expansions of the topic from a variety of
applications and viewpoints.

@@

\item
  The lesson is a beginning, not an end, for the learner

\item
  point them at similar material

\item
  and where to go next when they want to expand their knowledge.

\item
  A lesson is one piece of a larger engagement your learners are having
  with a topic. Enable their further engagement.
